\documentclass[10pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Authors of Proposal}
\title{Response to Committee }
\begin{document}
\maketitle
\section*{Physics Motivation}	
Work in progress. Intention to be completed by May 20, 2016.
\section*{Count Rate Estimates}	
Work in progress. Intention to be completed by May 20, 2016. However this issue needs clarification. Meeting has been requested. 
\section*{Measurement}	
Work in progress. Intention to be completed by May 20, 2016.
\section*{Simulation}	
Work in progress. Intention to be completed by May 20, 2016.
\section*{Preliminary G12 results}	
The authors have added more information about the g12 $\eta'$ analysis with regards to triggering, dilepton identification, sources of background and a summary of the Qfactor method. However, authors would like to point out that the Qfactor method was chosen for the g12 analysis as it is best suitable for low statics background subtraction.
\section*{Assorted typos rearrangements}
Most of these comments have been implemented in the new version. Here is a list of what was not implemented with the authors reasoning.
\begin{itemize}
	\item Comment about Figs. 4, 5.
	\begin{itemize}
		\item The contamination is a function of when a photon traverses through matter, therefore the distance of the traveling dileptons does not provide additional information.
	\end{itemize}
	\item Abstract: item b regarding 3rd paragraph
	\begin{itemize}
		\item Authors feel that this requested change does not fit well within the context of the writing style.
	\end{itemize}
		\item Motivation: item e regarding 3rd paragraph
	\begin{itemize}
		\item Authors understand that this statement is general. We also are unclear of what the committee is proposing.
	\end{itemize}
	\item Kinematics: item 2.1 regarding ``expectation'' $\to$ ``diagram''
	\begin{itemize}
		\item Authors feel that this change does not fit into the scope as it reads currently as ``An example of QED expectation for $\eta'$ is shown in...'', the change would have it read ``An example of QED diagram for $\eta'$ is shown in...''
	\end{itemize}
	\item Section 1.2: Regarding changing of title
	\begin{itemize}
		\item Authors feel that this section not only describes the history of Dalitz decays but also transition form factors and should stay with current title.
	\end{itemize}
	\item Section 2: Regarding changing of title
	\begin{itemize}
		\item Authors feel that this section describes the most probable kinematics that will be needed to measure the transition form factor and should stay with the title ``Kinematics''
	\end{itemize}
	\item Section 2.3: Regarding moving this section to ``Measurement'' 
	\begin{itemize}
		\item Authors feel that this section is properly placed as the section is to inform the reader about the possible contamination. Furthermore, the authors would like to stress that this contamination is not only manageable but is also not relevant when measuring the transition form factor as the deviation from QED is expected at high $M(e^+e^-)$ masses. 
	\end{itemize}
	\item Last comment in reference to removing figures 10-11 and 12 or 13.
	\begin{itemize}
		\item Authors have removed Figs. 10, 11. However, we feel that Figs. 12, 13 should remain as it is important to show that the acceptance of the $e^+e^-$ is independent of the decay kinematics.
	\end{itemize}
	\item Style of Tab. $\to$ Table was not implemented as it conflicts with AIP style.
\end{itemize}
\section*{Authors edits}
	\begin{itemize}
	\item An edit was performed on Appendix A. There were typos found.
	\end{itemize}
\end{document}